\subsection{TheFork}

TheFork is the smallest source but is highly restaurant-specific and already contains near-complete coordinates. Its ratings use a native 0-10 scale, so comparison with Google and Tripadvisor requires scale normalization.

\paragraph{Key metrics}
\begin{tabular}{lr}
\toprule
Metric & Value \\
\midrule
Records assessed & 1344 \\
Overall quality score & 97.63\% \\
Average field completeness & 76.15\% \\
Critical-field completeness & 98.88\% \\
Validity score & 100.00\% \\
Uniqueness score & 100.00\% \\
Timeliness score & 95.83\% \\
Collection duration & 2.00 h \\
Timestamp coverage & 100.00\% \\
Reliability score & 88.84\% \\
Format values checked & 21493 / 21493 valid \\
Native rating average & 8.86 \\
Comparable rating average 0--5 & 4.43 \\
Valid review counts & 1318 (98.07\%) \\
Low-review records & 117 (8.88\%) \\
Valid coordinate pairs & 1344 (100.00\%) \\
Latest source timestamp & 2026-06-06T20:35:04+00:00 \\
Data age in days & 2.55 \\
Quality flags & 229 (17.0 per 100 records) \\
\bottomrule
\end{tabular}

\paragraph{Weakest field coverage}
\begin{tabular}{lrrr}
\toprule
Field & Present & Missing & Coverage \\
\midrule
email & 0 & 1344 & 0.00\% \\
phone\_number & 0 & 1344 & 0.00\% \\
social\_links & 0 & 1344 & 0.00\% \\
website & 0 & 1344 & 0.00\% \\
discount & 650 & 694 & 48.36\% \\
opening\_hours & 855 & 489 & 63.62\% \\
rating & 1265 & 79 & 94.12\% \\
\bottomrule
\end{tabular}

\paragraph{Most frequent quality flags}
\begin{tabular}{lr}
\toprule
Issue type & Count \\
\midrule
low\_review\_count & 117 \\
missing\_critical\_field & 105 \\
zero\_reviews & 7 \\
\bottomrule
\end{tabular}

\paragraph{Interpretation}
\begin{itemize}
\item The weighted source quality score is 97.63\%; the score is driven by integration-critical fields rather than optional metadata.
\item The weakest fields are email (0.00\%), phone\_number (0.00\%), social\_links (0.00\%); downstream logic should avoid treating them as mandatory matching keys.
\item Format validity checks 21493 present values; 0 fail the expected source-specific format.
\item The sparse-review threshold flags 117 records, so rating comparisons should account for review-count reliability.
\item Timeliness score is 95.83\%, based on collection duration 2.00 h against a 48.00 h refresh target; timestamp coverage is 100.00\%.
\item The source has 229 generated quality flags, equal to 17.04 flags per 100 records.
\item TheFork is suitable for geospatial matching now, but its missing contact fields (website, social links, phone, and email) limit its usefulness for contact-based validation.
\end{itemize}
