\subsection{Tripadvisor}

Tripadvisor contributes broad review and category information, but the raw file does not yet contain latitude and longitude. It therefore needs the planned geocoding enrichment before reliable geospatial integration.

\paragraph{Key metrics}
\begin{tabular}{lr}
\toprule
Metric & Value \\
\midrule
Records assessed & 7539 \\
Overall quality score & 67.89\% \\
Average field completeness & 84.34\% \\
Critical-field completeness & 99.78\% \\
Validity score & 99.90\% \\
Uniqueness score & 99.97\% \\
Timeliness score & 0.00\% \\
Reliability score & 53.10\% \\
Native rating average & 3.91 \\
Comparable rating average 0--5 & 3.91 \\
Valid review counts & 7539 (100.00\%) \\
Low-review records & 2723 (36.12\%) \\
Valid coordinate pairs & 0 (0.00\%) \\
Latest source timestamp & n/a \\
Data age in days & n/a \\
Quality flags & 3621 (48.0 per 100 records) \\
\bottomrule
\end{tabular}

\paragraph{Weakest field coverage}
\begin{tabular}{lrrr}
\toprule
Field & Present & Missing & Coverage \\
\midrule
email & 3535 & 4004 & 46.89\% \\
opening\_hours & 5096 & 2443 & 67.60\% \\
price\_range & 5101 & 2438 & 67.66\% \\
cuisine\_type & 5859 & 1680 & 77.72\% \\
photo\_count & 5949 & 1590 & 78.91\% \\
website & 6023 & 1516 & 79.89\% \\
reviews & 6683 & 856 & 88.65\% \\
\bottomrule
\end{tabular}

\paragraph{Most frequent quality flags}
\begin{tabular}{lr}
\toprule
Issue type & Count \\
\midrule
low\_review\_count & 2723 \\
zero\_reviews & 813 \\
missing\_critical\_field & 81 \\
possible\_duplicate\_name\_address & 4 \\
\bottomrule
\end{tabular}

\paragraph{Interpretation}
\begin{itemize}
\item The weighted source quality score is 67.89\%; the score is driven by integration-critical fields rather than optional metadata.
\item The weakest fields are email (46.89\%), opening\_hours (67.60\%), price\_range (67.66\%); downstream logic should avoid treating them as mandatory matching keys.
\item The sparse-review threshold flags 2723 records, so rating comparisons should account for review-count reliability.
\item Timeliness coverage is 0.00\%; sources without record-level timestamps should be documented as stale-risk inputs.
\item The source has 3621 generated quality flags, equal to 48.03 flags per 100 records.
\item The 0\% coordinate validity is expected at this stage and should be resolved by the latitude/longitude enrichment task before integration.
\end{itemize}
