\chapter{Schema Integration and Analytical Storage}

After schema matching and entity resolution, the project materializes a unified
restaurant dataset. This stage is the point at which the three platform-specific
clean collections become a single integrated database suitable for quality
assessment and analytical querying.

\section{Construction of the Integrated Dataset}

The integration process is implemented as a MongoDB-to-MongoDB transformation. It
reads the three clean collections and the entity-resolution candidates:

\begin{itemize}
    \item \texttt{restaurants\_clean\_google};
    \item \texttt{restaurants\_clean\_tripadvisor};
    \item \texttt{restaurants\_clean\_thefork};
    \item \texttt{entity\_resolution\_candidates}.
\end{itemize}

The output consists of two collections:

\begin{itemize}
    \item \texttt{entity\_resolution\_links}, containing the selected one-to-one
    links between Google anchors and matched source records;
    \item \texttt{restaurants\_integrated}, containing the final integrated
    restaurant entities.
\end{itemize}

The effective candidate label is computed as:

\[
\texttt{effective\_label} =
\begin{cases}
\texttt{llm\_label}, & \text{if an LLM decision is available}\\
\texttt{label}, & \text{otherwise}
\end{cases}
\]

Only candidates whose effective label is \texttt{MATCH} are eligible for link
selection. Tripadvisor and TheFork links are selected independently, so an
integrated restaurant may contain only Google evidence, Google plus Tripadvisor,
Google plus TheFork, or all three platforms.

\section{Final Integrated Schema}

The integrated collection is Google-seeded: each document represents one dining
and operational Google restaurant. The document identifier is deterministic:

\[
\texttt{integrated\_restaurant\_id} = \texttt{"google:"} + \texttt{place\_id}
\]

Google is used as the canonical identity and geographic backbone because it has
the highest spatial coverage and complete coordinates. Non-Google sources are
attached as evidence blocks only when selected entity-resolution links exist.

\begin{table}[H]
\centering
\footnotesize
\begin{tabularx}{\textwidth}{p{0.28\textwidth}X}
\toprule
\textbf{Field group} & \textbf{Main attributes} \\
\midrule
Canonical identity and geography &
\texttt{integrated\_restaurant\_id}, \texttt{canonical\_name},
\texttt{canonical\_address}, \texttt{canonical\_city},
\texttt{latitude}, \texttt{longitude}. \\
Platform membership &
\texttt{has\_google}, \texttt{has\_tripadvisor}, \texttt{has\_thefork},
\texttt{platform\_count}. \\
Comparable ratings &
\texttt{google\_rating\_5}, \texttt{tripadvisor\_rating\_5},
\texttt{thefork\_rating\_5}, \texttt{rating\_avg\_5},
\texttt{rating\_range\_5}. \\
Review counts &
\texttt{google\_review\_count}, \texttt{tripadvisor\_review\_count}, \texttt{thefork\_review\_count}. \\
Contacts and price &
\texttt{website}, \texttt{phones}, \texttt{price\_level},
\texttt{price\_evidence}. \\
Cuisine and taxonomy &
\texttt{cuisine\_primary}, \texttt{cuisine\_tags}. \\
Audit and provenance &
\texttt{integration\_flags}, \texttt{sources.google},
\texttt{sources.tripadvisor}, \texttt{sources.thefork}. \\
\bottomrule
\end{tabularx}
\caption{Structure of the final \texttt{restaurants\_integrated} collection.}
\label{tab:integrated-schema-overview}
\end{table}

The schema deliberately preserves source-specific ratings rather than replacing
them with a single resolved value. This is a central design decision: the research
questions require measuring disagreement across platforms, therefore the
differences between Google, Tripadvisor, and TheFork must remain visible.

\section{Conflict Handling and Provenance}

Conflicts are resolved according to the role of each attribute. Canonical identity
and coordinates use a metadata-based strategy: Google is trusted as the anchor
source. Comparative values, such as ratings and review counts, are not resolved
away; they are kept side by side. Derived fields such as \texttt{rating\_avg\_5}
and \texttt{rating\_range\_5} summarize the comparison without hiding the source
values.

Contacts and price are handled differently. Phone values are preserved as a
deduplicated set because a restaurant may legitimately have multiple numbers.
Website conflicts keep the raw evidence and prefer Google only when conflicting
values cannot be reconciled. Price is a genuine value conflict, because the three
platforms may disagree on how expensive a restaurant is. Each source price is first
mapped to a shared ordinal tier expressed with human-readable labels
(\texttt{INEXPENSIVE}, \texttt{MODERATE}, \texttt{EXPENSIVE},
\texttt{VERY\_EXPENSIVE}). The top-level price level is then resolved by
majority-vote consensus across the available sources rather than by a fixed source
priority: the tier supported by the largest number of platforms wins. When two
tiers are equally supported, the conflict is not forced; the resulting value is a
sorted list of the tied labels, which deliberately preserves the signal that the
restaurant straddles price tiers across platforms. The original source-specific
price values remain available under the source blocks.

This design maintains reproducibility: every integrated top-level value can be
traced back to the original platform evidence stored under
\texttt{sources.google}, \texttt{sources.tripadvisor}, and
\texttt{sources.thefork}.

\section{Cuisine Reconciliation}
\label{sec:cuisine-reconciliation}

Cuisine was the most heterogeneous descriptor to integrate, and it is resolved
explicitly during the construction of the integrated dataset. The three sources
express cuisine in three unreconciled vocabularies: Tripadvisor uses Italian
feminine adjectives (\textit{Italiana}, \textit{Asiatica}), TheFork uses masculine
adjectives (\textit{Italiano}, \textit{Asiatico}) together with many regional
Italian labels (\textit{Lombardo}, \textit{Toscano}, \textit{Napoletano}), while
Google exposes an English controlled vocabulary
(\texttt{italian\_restaurant}, \texttt{pizza\_restaurant}) that covers almost every
venue but is dominated by non-food types. A first version of the integration kept
only the first cuisine label of each venue, which split a single cuisine across
several rows and ignored Google's near-complete coverage. The reconciliation step
was introduced to remove this bias.

The reconciliation is implemented as an explicit, hand-built canonical taxonomy
rather than automatic stemming. Stemming cannot translate Google's English labels
and would incorrectly merge unrelated terms such as \textit{Pesce} (fish) and
\textit{Pizza}, whereas an explicit map also documents each judgement call and keeps
the step auditable. The map is derived from the complete exploded inventory of all
observed labels across the three platforms (51 Tripadvisor labels, 57 TheFork
labels, and roughly 130 Google food types) and assigns every raw label to a small
set of canonical buckets. Regional Italian labels collapse into \textit{Italian},
and cross-language variants such as \textit{Italiana}, \textit{Italiano}, and
\texttt{italian\_restaurant} converge onto the same bucket.

Because most venues carry several cuisines, the reconciliation is multi-label. The
union of canonical buckets observed across the three platforms is kept as
\texttt{cuisine\_tags}, while a single \texttt{cuisine\_primary} is derived for
analyses that require one point per venue. The primary bucket is chosen through a
specificity-ranked consensus: the most specific bucket wins, so \textit{Pizza}
takes precedence over the umbrella \textit{Italian} and \textit{Chinese} over the
umbrella \textit{Asian}. Ties are broken by source precedence, preferring
Tripadvisor over TheFork and TheFork over Google. An agreement indicator records
whether the platforms concur on the venue's cuisine. This reconciliation is the
data-management step that later allows the research-question analysis to group
restaurants on a single trustworthy cuisine bucket instead of raw, gendered, or
language-specific labels.

\section{Post-Integration Quality Assessment}
\label{sec:post-integration-quality}

The quality of the integration was evaluated against the same manually labelled
gold standard described in the entity-resolution chapter, comparing the pipeline's
automatic decisions with the human \texttt{MATCH}/\texttt{NON\_MATCH} labels. The
assessment measures not only the entity-resolution classifier, but also the
survival of one-to-one selected links through the integration step and the spatial
enrichment of Tripadvisor records, so that the final integrated dataset is judged
end to end rather than only at the matching stage.

\begin{table}[H]
\centering
\footnotesize
\begin{tabular}{p{0.55\textwidth}r}
\toprule
\textbf{Metric} & \textbf{Value} \\
\midrule
Out-of-sample evaluation rows & 288 \\
In-calibration labelled rows & 600 \\
MATCH precision & 96.8\% \\
Strict MATCH recall & 71.7\% \\
MATCH-or-UNCERTAIN kept recall & 100.0\% \\
Uncertain rate & 33.0\% \\
Selected links from human-confirmed matches & 88 / 127 \\
Link survival rate & 69.3\% \\
Integration survival rate & 69.3\% \\
Median Tripadvisor geocoding error & 10.1 m \\
Tripadvisor coordinates within 50 m & 91.3\% \\
Tripadvisor coordinate coverage & 84.0\% \\
\bottomrule
\end{tabular}
\caption{Post-integration assessment of entity resolution, link selection, and Tripadvisor geocoding.}
\label{tab:post-integration-quality}
\end{table}

The results show a conservative integration policy. Precision is high, meaning
that automatic matches are rarely wrong. Strict recall is lower because many
true matches are intentionally left as \texttt{UNCERTAIN} rather than forced into
unsafe automatic links. This behaviour is desirable in a data integration
setting: false positives would contaminate the final dataset more severely than
unresolved candidates.

The survival rate quantifies the effect of one-to-one selection. Some
human-confirmed matches are not present in the final integrated source blocks
because conservative link selection removes ambiguous alternatives. The geocoding
assessment confirms that Tripadvisor spatial enrichment is reliable enough for
blocking and spatial analysis: the median error is 10.1 m and all evaluated gold
rows are within 100 m. The supporting gold-sample counts, metric definitions,
survival tables, and geocoding-error diagnostics are included in
Appendix~\ref{app:post-integration-assessment}.

\section{ClickHouse Analytical Layer}

MongoDB is well suited for raw and integrated document storage, but the final
research questions require repeated aggregations, pairwise rating comparisons,
ranking, grouping by geographic area, and correlation-style summaries. For this
reason, the project adds ClickHouse as a column-oriented analytical DBMS.

The ClickHouse loader reads the cleaned and integrated MongoDB collections and
creates four flat analytical tables:

\begin{itemize}
    \item \texttt{restaurants\_integrated};
    \item \texttt{restaurants\_clean\_google};
    \item \texttt{restaurants\_clean\_tripadvisor};
    \item \texttt{restaurants\_clean\_thefork}.
\end{itemize}

The load process is reproducible and idempotent: each run creates the destination
tables if needed, truncates them, and reloads the current MongoDB state. The
integrated table keeps the analytical columns needed for the research questions,
including platform ratings, review counts, platform membership flags, normalized
price tier, the canonical cuisine fields (\texttt{cuisine\_primary} and
\texttt{cuisine\_tags}) produced by the reconciliation step, photo counts, and
geographic coordinates. Heavy nested
evidence remains in MongoDB, while ClickHouse stores a flat projection optimized
for SQL analysis.

The design therefore separates responsibilities:

\begin{itemize}
    \item MongoDB stores raw, clean, integrated, and auditable document data;
    \item ClickHouse stores flat analytical tables for fast, reproducible queries;
    \item the notebook reads from ClickHouse without modifying either database.
\end{itemize}

This two-layer architecture satisfies the project requirement of modelling and
storing integrated data in DBMSs while also providing an efficient surface for the
final research-question analysis.
