\documentclass[12pt,a4paper]{report}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{graphicx}
\usepackage{geometry}
\usepackage{longtable}
\usepackage{booktabs}
\usepackage{caption}
\usepackage{amsmath}
\usepackage{float}
\usepackage{tabularx} 
\usepackage{array}
\usepackage{ragged2e}
\usepackage{xcolor}

\definecolor{qualityblue}{RGB}{31,119,180}
\definecolor{qualitygreen}{RGB}{44,160,44}
\definecolor{qualityorange}{RGB}{255,127,14}
\definecolor{qualityred}{RGB}{214,39,40}
\definecolor{qualitygray}{RGB}{127,127,127}

\geometry{margin=2.5cm}

\usepackage{setspace}
\onehalfspacing

% Avoid overfull lines caused by long unbreakable \texttt{} identifiers
\setlength{\emergencystretch}{3em}

\usepackage{hyperref}
\hypersetup{
colorlinks=true,
linkcolor=black,
urlcolor=blue
}

\begin{document}

% Copertina
\input{cover}

% Abstract
\input{abstract}
\newpage

% Indice
\tableofcontents
\newpage

% Introduzione
\input{introduction}

% Capitoli
\input{chapter1}

\input{chapter2}

\input{chapter3}

\input{chapter4}

\input{chapter5}

\input{chapter6}

% Conclusioni
\input{conclusions}

% Riferimenti / Repository
\chapter*{References}
\addcontentsline{toc}{chapter}{References}

\noindent\textbf{Project repository.} Full source code and reproducible Docker
infrastructure: \url{https://github.com/Laimon99/data-management-project}.

\vspace{0.6em}
\noindent\textbf{Data sources and APIs.}
\begin{itemize}\setlength{\itemsep}{2pt}
    \item Google Maps Platform --- Places API. \url{https://developers.google.com/maps/documentation/places/web-service}
    \item Tripadvisor. \url{https://www.tripadvisor.com/}
    \item TheFork. \url{https://www.thefork.com/}
    \item OpenStreetMap and the Nominatim geocoding service. \url{https://www.openstreetmap.org/} --- \url{https://nominatim.org/}
\end{itemize}

\noindent\textbf{Databases and infrastructure.}
\begin{itemize}\setlength{\itemsep}{2pt}
    \item MongoDB documentation. \url{https://www.mongodb.com/docs/}
    \item ClickHouse documentation. \url{https://clickhouse.com/docs}
    \item Docker documentation. \url{https://docs.docker.com/}
    \item Python. \url{https://www.python.org/} --- uv package manager. \url{https://docs.astral.sh/uv/}
\end{itemize}

\noindent\textbf{Main libraries.}
\begin{itemize}\setlength{\itemsep}{2pt}
    \item Playwright for Python (web scraping). \url{https://playwright.dev/python/}
    \item RapidFuzz (fuzzy string matching). \url{https://rapidfuzz.github.io/RapidFuzz/}
    \item GeoPy (geocoding client). \url{https://geopy.readthedocs.io/}
    \item PyMongo and ClickHouse Connect (database drivers). \url{https://pymongo.readthedocs.io/} --- \url{https://clickhouse.com/docs/integrations/python}
    \item Pydantic (settings and validation). \url{https://docs.pydantic.dev/}
    \item pandas, SciPy and Plotly (analysis and visualization). \url{https://pandas.pydata.org/} --- \url{https://scipy.org/} --- \url{https://plotly.com/python/}
\end{itemize}

\noindent\textbf{Methodological references.}
\begin{itemize}\setlength{\itemsep}{2pt}
    \item E.~Rahm and P.~A.~Bernstein. \textit{A survey of approaches to automatic schema matching.} The VLDB Journal, 10(4):334--350, 2001.
    \item P.~Christen. \textit{Data Matching: Concepts and Techniques for Record Linkage, Entity Resolution, and Duplicate Detection.} Springer, 2012.
    \item C.~Batini and M.~Scannapieco. \textit{Data and Information Quality: Dimensions, Principles and Techniques.} Springer, 2016.
\end{itemize}

% Appendici
\appendix
\input{appendix}

\end{document}
