\subsection{Tripadvisor}

Tripadvisor contributes broad review and category information, but the raw file does not yet contain latitude and longitude or record-level timestamps. Its lower raw score is expected and should be improved through the planned cleaning and geocoding enrichment before reliable geospatial integration.

\paragraph{Key metrics}
\begin{tabular}{lr}
\toprule
Metric & Value \\
\midrule
Records assessed & 7539 \\
Overall quality score & 72.28\% \\
Average field completeness & 84.34\% \\
Critical-field completeness & 99.78\% \\
Validity score & 99.99\% \\
Uniqueness score & 99.97\% \\
Timeliness score & 43.75\% \\
Collection duration & 27.00 h \\
Timestamp coverage & 0.00\% \\
Reliability score & 53.10\% \\
Format values checked & 82654 / 82655 valid \\
Native rating average & 3.91 \\
Comparable rating average 0--5 & 3.91 \\
Valid review counts & 7539 (100.00\%) \\
Low-review records & 2723 (36.12\%) \\
Valid coordinate pairs & 0 (0.00\%) \\
Latest source timestamp & n/a \\
Data age in days & n/a \\
Quality flags & 3622 (48.0 per 100 records) \\
\bottomrule
\end{tabular}

\paragraph{Weakest field coverage}
\begin{tabular}{lrrr}
\toprule
Field & Present & Missing & Coverage \\
\midrule
email & 3535 & 4004 & 46.89\% \\
opening\_hours & 5096 & 2443 & 67.60\% \\
price\_range & 5101 & 2438 & 67.66\% \\
cuisine\_type & 5859 & 1680 & 77.72\% \\
photo\_count & 5949 & 1590 & 78.91\% \\
website & 6023 & 1516 & 79.89\% \\
reviews & 6683 & 856 & 88.65\% \\
\bottomrule
\end{tabular}

\paragraph{Most frequent quality flags}
\begin{tabular}{lr}
\toprule
Issue type & Count \\
\midrule
low\_review\_count & 2723 \\
zero\_reviews & 813 \\
missing\_critical\_field & 81 \\
possible\_duplicate\_name\_address & 4 \\
invalid\_field\_format & 1 \\
\bottomrule
\end{tabular}

\paragraph{Interpretation}
\begin{itemize}
\item The weighted source quality score is 72.28\%; the score is driven by integration-critical fields rather than optional metadata.
\item The weakest fields are email (46.89\%), opening\_hours (67.60\%), price\_range (67.66\%); downstream logic should avoid treating them as mandatory matching keys.
\item Format validity checks 82655 present values; 1 fail the expected source-specific format.
\item The sparse-review threshold flags 2723 records, so rating comparisons should account for review-count reliability.
\item Timeliness score is 43.75\%, based on collection duration 27.00 h against a 48.00 h refresh target; timestamp coverage is 0.00\%.
\item The source has 3622 generated quality flags, equal to 48.04 flags per 100 records.
\item The 0\% coordinate validity is expected at this stage and should be resolved by the latitude/longitude enrichment task before integration.
\item The missing record-level timestamps do not force timeliness to 0 anymore; Tripadvisor refreshability is estimated from the scraper runtime instead.
\end{itemize}
