\documentclass[11pt,a4paper]{article}

\usepackage[margin=2.5cm]{geometry}
\usepackage{booktabs}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

\title{Post-Integration Assessment of Restaurant Data Integration}
\author{Data Management Project}
\date{\today}

\begin{document}
\maketitle

\section{Scope}

This report evaluates the automated integration and enrichment steps after
cleaning, entity resolution, one-to-one link selection, and unified dataset
construction. The assessment uses hand-labeled candidate pairs as a gold
standard and measures both classifier error and end-to-end survival into the
integrated collection.

\subsection*{Gold Sample Counts}

\input{tables/gold_sample_counts.tex}

\section{Metric Definitions}

\input{tables/metric_definitions.tex}

\section{Entity Resolution Classifier}

The classifier metrics compare the shipped MongoDB candidate labels against the
out-of-sample hand-labeled gold rows passed with \texttt{--gold-csv}. Manual LLM
labels are treated as overrides when present. Labels passed with
\texttt{--in-calibration-gold-csv} are used for the calibration and
cross-validation block in the generated Markdown report, not for the
out-of-sample score table.

\input{tables/er_metrics.tex}

\section{End-to-End Integration Survival}

This section measures whether human-confirmed matches survived beyond
classification into selected one-to-one links and integrated restaurant source
blocks.

\input{tables/end_to_end_survival.tex}

\section{Spatial Enrichment}

Tripadvisor spatial enrichment is measured by comparing geocoded Tripadvisor
coordinates against the Google seed coordinates for human-confirmed matches.
Observed distances are truncated by the entity-resolution blocking radius:
gross geocoding failures usually appear as missed matches, missing coordinate
coverage, or unblockable candidates rather than large distance rows.

\input{tables/geocoding_error.tex}

\section{Generated Artifacts}

The full structured metrics, inspection CSVs, Markdown narrative, and
report-ready LaTeX tables are regenerated by
\texttt{uv run integration-assessment}. This PDF imports the generated tables
from the post-integration report folder.

\end{document}
